A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-12-02 bioc-workflow.tex
updates based on Claire's comments - up to p10

Installation of Bioconductor package is documented in detail on the
\href{http://bioconductor.org/install/#install-bioconductor-packages}{Bioconductor
  installation help page}. This procedure is also applicable to any
packages, from \href{https://cran.r-project.org/}{CRAN} as well as
GitHub. Once a package has been installed, it needs to be loaded for
its functionality to become available in the R session; this is done
with the \texttt{library} function e.g.  to load the
\Biocpkg{pRoloc} one would type \texttt{library("pRoloc")}
after installation.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{fvarLabels}\hlstd{(hl)}
\end{alltt}
\begin{verbatim}
##  [1] "X"                                
##  [2] "X.1"                              
##  [3] "X.2"                              
##  [4] "Experiment.1"                     
##  [5] "Experiment.2"                     
##  [6] "Experiment.1.1"                   
##  [7] "Experiment.2.1"                   
##  [8] "phenoDisco.Input"                 
##  [9] "phenoDisco.Output"                
## [10] "Curated.phenoDisco.Output"        
## [11] "SVM.marker.set"                   
## [12] "SVM.classification"               
## [13] "SVM.score"                        
## [14] "SVM.classification..top.quartile."
## [15] "Final.Localization.Assignment"    
## [16] "First.localization.evidence."     
## [17] "Curated.Organelles"               
## [18] "Cytoskeletal.Components"          
## [19] "Trafficking.Proteins"             
## [20] "Protein.Complexes"                
## [21] "Signaling.Cascades"               
## [22] "Oct4.Interactome"                 
## [23] "Nanog.Interactome"                
## [24] "Sox2.Interactome"                 
## [25] "Cell.Surface.Proteins"
\end{verbatim}
\begin{alltt}
\hlkwd{fvarLabels}\hlstd{(hl)[}\hlnum{1}\hlopt{:}\hlnum{3}\hlstd{]} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"uniprot.accession"}\hlstd{,} \hlstr{"uniprot.id"}\hlstd{,} \hlstr{"description"}\hlstd{)}
\hlkwd{fvarLabels}\hlstd{(hl)[}\hlnum{4}\hlopt{:}\hlnum{6}\hlstd{]} \hlkwb{<-} \hlkwd{paste0}\hlstd{(}\hlstr{"peptides.expt"}\hlstd{,} \hlnum{1}\hlopt{:}\hlnum{3}\hlstd{)}
\hlkwd{fData}\hlstd{(hl)[}\hlnum{1}\hlopt{:}\hlnum{4}\hlstd{,} \hlnum{1}\hlopt{:}\hlnum{6}\hlstd{]}
\end{alltt}
\begin{verbatim}
##          uniprot.accession  uniprot.id
## Q9JHU4              Q9JHU4 DYHC1_MOUSE
## Q9QXS1-3          Q9QXS1-3  PLEC_MOUSE
## Q9ERU9              Q9ERU9  RBP2_MOUSE
## P26039              P26039  TLN1_MOUSE
##                                                                                                                                 description
## Q9JHU4                                              Cytoplasmic dynein 1 heavy chain 1 OS=Mus musculus GN=Dync1h1 PE=1 SV=2 - [DYHC1_MOUSE]
## Q9QXS1-3 Isoform PLEC-1 of Plectin OS=Mus musculus GN=Plec - [PLEC_MOUSE]|Isoform PLEC-1A of Plectin OS=Mus musculus GN=Plec - [PLEC_MOUSE]
## Q9ERU9                                                     E3 SUMO-protein ligase RanBP2 OS=Mus musculus GN=Ranbp2 PE=1 SV=2 - [RBP2_MOUSE]
## P26039                                                                             Talin-1 OS=Mus musculus GN=Tln1 PE=1 SV=2 - [TLN1_MOUSE]
##          peptides.expt1 peptides.expt2 peptides.expt3
## Q9JHU4              175            166            322
## Q9QXS1-3            123            150            174
## Q9ERU9              101             90            181
## P26039              101             94            167
\end{verbatim}
\end{kframe}
\end{knitrout}

Note that when using the simple \texttt{readMSnSet2} procedure, the \texttt{pData}
slot which is used to store information about the samples/channels
is kept empty. It is advised to annotate the channels as
well. Below, we annotate the replicate from which the profiles
originate and the TMT tag (extracted from the sample/channel names).

@@

Below, we update the replicate specific feature variable names and
remove the shared annotation.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{fvarLabels}\hlstd{(hyperLOPIT2015ms3r1)[}\hlnum{3}\hlopt{:}\hlnum{5}\hlstd{]} \hlkwb{<-} \hlkwd{paste0}\hlstd{(}\hlkwd{fvarLabels}\hlstd{(hyperLOPIT2015ms3r1)[}\hlnum{3}\hlopt{:}\hlnum{5}\hlstd{],} \hlnum{1}\hlstd{)}
\hlkwd{fvarLabels}\hlstd{(hyperLOPIT2015ms3r2)[}\hlnum{3}\hlopt{:}\hlnum{5}\hlstd{]} \hlkwb{<-} \hlkwd{paste0}\hlstd{(}\hlkwd{fvarLabels}\hlstd{(hyperLOPIT2015ms3r2)[}\hlnum{3}\hlopt{:}\hlnum{5}\hlstd{],} \hlnum{2}\hlstd{)}
\hlkwd{fData}\hlstd{(hyperLOPIT2015ms3r1)} \hlkwb{<-} \hlkwd{fData}\hlstd{(hyperLOPIT2015ms3r1)[}\hlnum{1}\hlopt{:}\hlnum{5}\hlstd{]}
\hlkwd{fData}\hlstd{(hyperLOPIT2015ms3r2)} \hlkwb{<-} \hlkwd{fData}\hlstd{(hyperLOPIT2015ms3r2)[}\hlnum{3}\hlopt{:}\hlnum{5}\hlstd{]}
\hlkwd{fvarLabels}\hlstd{(hyperLOPIT2015ms3r1)}
\end{alltt}
\begin{verbatim}
## [1] "EntryName"          "ProteinDescription" "Peptides1"         
## [4] "PSMs1"              "ProteinCoverage1"
\end{verbatim}
\begin{alltt}
\hlkwd{fvarLabels}\hlstd{(hyperLOPIT2015ms3r2)}
\end{alltt}
\begin{verbatim}
## [1] "Peptides2"        "PSMs2"            "ProteinCoverage2"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Thu Dec  1 10:49:34 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

More details above combining data are given in the dedicated
\textit{Combining MSnSet instances} section of the \Biocpkg{MSnbase}
\href{http://bioconductor.org/packages/release/bioc/vignettes/MSnbase/inst/doc/MSnbase-demo.pdf}{tutorial
  vignette}.

@@

We prefer to remove proteins that were not assayed in both replicated
experiments. This is done with the \texttt{filterNA} function that
removes features (proteins) that contain more than a certain proportion (default
is 0) missing values.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Thu Dec  1 10:49:34 2016 
## Subset [6725,20][5032,20] Thu Dec  1 10:49:35 2016 
## Removed features with more than 0 NAs: Thu Dec  1 10:49:35 2016 
## Dropped featureData's levels Thu Dec  1 10:49:35 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Thu Dec  1 10:49:37 2016 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Thu Dec  1 10:49:38 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Thu Dec  1 10:49:37 2016 
## Added markers from  'pdres' marker vector. Thu Dec  1 10:49:38 2016 
##  MSnbase version: 2.1.4
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{)}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4343505               0.3047508               0.3888373 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6858101               0.5897977               0.4283659 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4175965               0.5981079               0.9494104 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7967111               0.7085718               0.3154399 
##         Plasma membrane              Proteasome 
##               0.7107861               0.4112064
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      85                     171                      88 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     296                     473                      95 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      26                     124                     523 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     229                     344                      39 
##         Plasma membrane              Proteasome                 unknown 
##                     323                     158                    2058
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

Installation of Bioconductor package is documented in detail on the
\href{http://bioconductor.org/install/#install-bioconductor-packages}{Bioconductor
  installation help page}. Below, we show how to install the four main
packages used in this workflow:

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{source}\hlstd{(}\hlstr{"https://bioconductor.org/biocLite.R"}\hlstd{)}
\hlkwd{biocLite}\hlstd{(}\hlkwd{c}\hlstd{(}\hlstr{"MSnase"}\hlstd{,} \hlstr{"pRoloc"}\hlstd{,} \hlstr{"pRolocdata"}\hlstd{,} \hlstr{"pRolocGUI"}\hlstd{))}
\end{alltt}
\end{kframe}
\end{knitrout}

This procedure is also applicable to any packages, from
\href{https://cran.r-project.org/}{CRAN} as well as GitHub. Once a
package has been installed, it needs to be loaded for its
functionality to become available in the R session; this is done with
the \texttt{library} function e.g.  to load the \Biocpkg{pRoloc} one
would type \texttt{library("pRoloc")} after installation.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{fvarLabels}\hlstd{(hl)}
\end{alltt}
\begin{verbatim}
##  [1] "X"                                
##  [2] "X.1"                              
##  [3] "X.2"                              
##  [4] "Experiment.1"                     
##  [5] "Experiment.2"                     
##  [6] "Experiment.1.1"                   
##  [7] "Experiment.2.1"                   
##  [8] "phenoDisco.Input"                 
##  [9] "phenoDisco.Output"                
## [10] "Curated.phenoDisco.Output"        
## [11] "SVM.marker.set"                   
## [12] "SVM.classification"               
## [13] "SVM.score"                        
## [14] "SVM.classification..top.quartile."
## [15] "Final.Localization.Assignment"    
## [16] "First.localization.evidence."     
## [17] "Curated.Organelles"               
## [18] "Cytoskeletal.Components"          
## [19] "Trafficking.Proteins"             
## [20] "Protein.Complexes"                
## [21] "Signaling.Cascades"               
## [22] "Oct4.Interactome"                 
## [23] "Nanog.Interactome"                
## [24] "Sox2.Interactome"                 
## [25] "Cell.Surface.Proteins"
\end{verbatim}
\begin{alltt}
\hlkwd{fvarLabels}\hlstd{(hl)[}\hlnum{1}\hlopt{:}\hlnum{3}\hlstd{]} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"uniprot.accession"}\hlstd{,} \hlstr{"uniprot.id"}\hlstd{,} \hlstr{"description"}\hlstd{)}
\hlkwd{fvarLabels}\hlstd{(hl)[}\hlnum{4}\hlopt{:}\hlnum{6}\hlstd{]} \hlkwb{<-} \hlkwd{paste0}\hlstd{(}\hlstr{"peptides.expt"}\hlstd{,} \hlnum{1}\hlopt{:}\hlnum{3}\hlstd{)}
\hlcom{## feature vars 1, 2, and 4 to 6}
\hlkwd{fData}\hlstd{(hl)[}\hlnum{1}\hlopt{:}\hlnum{4}\hlstd{,} \hlkwd{c}\hlstd{(}\hlnum{1}\hlopt{:}\hlnum{2}\hlstd{,} \hlnum{4}\hlopt{:}\hlnum{6}\hlstd{)]}
\end{alltt}
\begin{verbatim}
##          uniprot.accession  uniprot.id peptides.expt1 peptides.expt2
## Q9JHU4              Q9JHU4 DYHC1_MOUSE            175            166
## Q9QXS1-3          Q9QXS1-3  PLEC_MOUSE            123            150
## Q9ERU9              Q9ERU9  RBP2_MOUSE            101             90
## P26039              P26039  TLN1_MOUSE            101             94
##          peptides.expt3
## Q9JHU4              322
## Q9QXS1-3            174
## Q9ERU9              181
## P26039              167
\end{verbatim}
\end{kframe}
\end{knitrout}

Note that when using the simple \texttt{readMSnSet2} procedure, the
\texttt{pData} slot which is used to store information about the
samples/channels is kept empty. As illustrated below, one can use the
\texttt{\$} operator to access (or create) individual columns in the
metadata slot. It is advised to annotate the channels as well. Below,
we annotate the replicate from which the profiles originate and the
TMT tag (extracted from the sample/channel names). To do so, we use
the sample names that were assigned automatically using the
quantiation column names and remove leading \texttt{X} and trailing
\texttt{.1} using the \texttt{sub} function.

@@

Below, we update the replicate specific feature variable names and
remove the shared annotation. In the first line, we update only the
feature variable names 3 to 5 (by appending a \texttt{1}) and in the
second line, we apply the \texttt{updateFvarLabels} function to update
all feature variable names (by appending a \texttt{2}).

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{fvarLabels}\hlstd{(hyperLOPIT2015ms3r1)[}\hlnum{3}\hlopt{:}\hlnum{5}\hlstd{]} \hlkwb{<-} \hlkwd{paste0}\hlstd{(}\hlkwd{fvarLabels}\hlstd{(hyperLOPIT2015ms3r1)[}\hlnum{3}\hlopt{:}\hlnum{5}\hlstd{],} \hlnum{1}\hlstd{)}
\hlstd{hyperLOPIT2015ms3r2} \hlkwb{<-} \hlkwd{updateFvarLabels}\hlstd{(hyperLOPIT2015ms3r2,} \hlstr{"2"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{)}
\hlkwd{fData}\hlstd{(hyperLOPIT2015ms3r1)} \hlkwb{<-} \hlkwd{fData}\hlstd{(hyperLOPIT2015ms3r1)[}\hlnum{1}\hlopt{:}\hlnum{5}\hlstd{]}
\hlkwd{fData}\hlstd{(hyperLOPIT2015ms3r2)} \hlkwb{<-} \hlkwd{fData}\hlstd{(hyperLOPIT2015ms3r2)[}\hlnum{3}\hlopt{:}\hlnum{5}\hlstd{]}
\hlkwd{fvarLabels}\hlstd{(hyperLOPIT2015ms3r1)}
\end{alltt}
\begin{verbatim}
## [1] "EntryName"          "ProteinDescription" "Peptides1"         
## [4] "PSMs1"              "ProteinCoverage1"
\end{verbatim}
\begin{alltt}
\hlkwd{fvarLabels}\hlstd{(hyperLOPIT2015ms3r2)}
\end{alltt}
\begin{verbatim}
## [1] "Peptides2"        "PSMs2"            "ProteinCoverage2"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Fri Dec  2 17:06:03 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

More details about combining data are given in the dedicated
\textit{Combining MSnSet instances} section of the \Biocpkg{MSnbase}
\href{http://bioconductor.org/packages/release/bioc/vignettes/MSnbase/inst/doc/MSnbase-demo.pdf}{tutorial
  vignette}.

@@

We prefer to remove proteins that were not assayed in both replicated
experiments. This is done with the \texttt{filterNA} function that
removes features (proteins) that contain more than a certain
proportion (default is 0) missing values. The \textit{Processing
  information} section summarises how combining and filtering missing
values (subsetting) changed the dimensions of the data.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Fri Dec  2 17:06:03 2016 
## Subset [6725,20][5032,20] Fri Dec  2 17:06:04 2016 
## Removed features with more than 0 NAs: Fri Dec  2 17:06:04 2016 
## Dropped featureData's levels Fri Dec  2 17:06:04 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Fri Dec  2 17:06:06 2016 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Fri Dec  2 17:06:07 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Fri Dec  2 17:06:05 2016 
## Added markers from  'pdres' marker vector. Fri Dec  2 17:06:07 2016 
##  MSnbase version: 2.1.4
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{)}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4350585               0.3020114               0.3827713 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6916987               0.5981016               0.4325049 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4337431               0.5912701               0.9497307 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7942905               0.7137491               0.3148182 
##         Plasma membrane              Proteasome 
##               0.7173760               0.4123604
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      86                     169                      88 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     297                     477                      98 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      28                     123                     522 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     230                     342                      39 
##         Plasma membrane              Proteasome                 unknown 
##                     318                     158                    2057
\end{verbatim}
\end{kframe}
\end{knitrout}
